Data preparation for employee category analysis

### 2023-04-24 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Finishing team mode and starting colocation

#### Proportion of working days co-located with at least one other team member
#### Proportion of working days co-located with supervisor
#### Proportion of working days co-located with entire team
#### Proportion of working days entire team is remote

>>>>

Calculate the mode team size for each employee.

```{r}
prep_xx <- 
  prep_b %>% 
  group_by(person_id) %>% 
  summarise(team_size_mode = getmode(team_size)) %>% 
  ungroup()
```

#### Proportion of working days co-located with at least one other team member

```{r}
prep_a <- 
  cohort_panel %>% 
  filter(daily_status_imputed)
  select
```

#### Proportion of working days co-located with supervisor
#### Proportion of working days co-located with entire team
#### Proportion of working days entire team is remote
